Constraining gravitational wave amplitude birefringence and Chern-Simons gravity with GWTC-3

### 2022-06-28 src/tex/ms.tex
Update ms.tex
Insert points for some sections and content for method

\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

@@

\citep{Maria_2021}.

@@

@@

@@

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{amsfonts,amssymb,amsmath}

@@

Beyond-GR theory\\
Birefringence\\
\citep{Maria_2021}

Bilby\\
Bayesian

@@

Mentioned above, the amount of amplitude birefringence is represented by the opacity parameter $\kappa$.
We performed estimation on $\kappa$ by Bilby with data from the GWTC catalog to constrain the plausible range of $\kappa$.

To implement the amplitude birefringence on Bilby, waveforms generated by different approximants are modified according to the following equation:
\begin{equation}
    h_{L,R}^{\textrm{new}}\left(f\right)=
    h_{L,R}^{\textrm{old}}\left(f\right)\times
    \exp\left(\pm\kappa\frac{d_C}{1\textrm{ Gpc}}\frac{f}{0.1\textrm{ kHz}}\right)
\end{equation}, where $h_{L,R}$ is the amplitude of the left or right polarization of the generated waveform
, $\kappa$ is the dimensionless opacity parameter, $d_C$ is the comoving distance, and $f$ is the frequency of the generated waveform.

Bilby will then perform estimation on the original gravitational wave parameters as well as $\kappa$.

@@

GWTC-3

@@

Limitation\\
orientation
sensitivity

Future Study\\
Data from more detectors
